The Social Conditioning of Fear

### 2023-12-06 scripts/manuscript.qmd
gender variable

Especially, the role of gender in fear of crime has been well documented in victimization research [@cops2011; @snedker2006; @schnitzer2010].

[@stanko1993]

>>>>

Especially, the role of gender in fear of crime has been well documented in victimization research [@cops2011; @snedker2006; @schnitzer2010; @stanko1993]. Early scholarship emphasized that women tend to report more fear than men  [@stanko1990], with some initial research investigating the seeming disjuncture between women's fear and their actual experiences of victimization, as women were often found to report high levels of fear for crimes that they were at relatively little risk of experiencing [@hough1983]. Subsequent studies suggested that women's fear should be understood in the context of the many potential threats that women confront, including their heightened risk of sexual assault [@stanko1993]. Therefore, fear at night is gradually perceived as a manifestation of gender-based violence with sexual assault implications, though acknowledging that sexual assault is merely one among many potential forms of crime.
